---
title: "Risk Assessment Report"
output: flexdashboard::flex_dashboard

---

```{r resources, include=FALSE}
library(flexdashboard)
library(plyr)
library(googledrive)
library(ggplot2)
library(scales)
library(reshape2)
library(viridis)
library(httpuv)
library(ggridges)
library(readxl)
library(plotly)
library(dplyr)
library(formattable)
library(sparkline)
library(plotly)
library(stringr)
library(ggbeeswarm)
library(kableExtra)
library(leaflet)

source("rpert.R")
source("monterlo.R")
set.seed(3141593)

# If having Pandoc errors you may need to create a file that explicitly tells R where to launch from. This will happen if you have a weird install or are using a virtual workstation etc.
# Sys.getenv('R_USER')
# .Renviron file in H:/ and included in it the single entry R_USER=H:/
```

```{r parameters, include=FALSE}
# Activate any custom functions/modules source
# Set ####
  # Set number of simulation permutations (at least 10,000 recommended)
  n_perms = 500

  drive_auth(email = "cneskey@gmail.com")
  drive_user()
  # Identify the sheet of interest
  gsheet_name <- drive_get("https://docs.google.com/spreadsheets/d/1DWB4rdAmUGggkUN0KtVdtyn6E1gZ9j68QifDD8cn2fY/edit#gid=1658565121")
  # Download the sheet as 'download_temp', overwrite if present.
  drive_download(gsheet_name, path = "downloaded_temp", overwrite = TRUE)


```
  
```{r preprocessing, include=FALSE}
# read the "api_stages" sheets into memory.
  gEstimates <- read_excel("downloaded_temp.xlsx", sheet = "api_stage", skip = 10)
  gEstimates2 <- read_excel("downloaded_temp.xlsx", sheet = "api_stage_2", skip = 9)
  gScope <- read_excel("downloaded_temp.xlsx", sheet = "Scope", skip = 3)
  
# Sim ----
# Define unique identifier variables
  n_scens = length(na.omit(gEstimates$`UID`))
  n_bens = length(na.omit(gEstimates2$`Benefit UID`))
  n_costs = length(na.omit(gEstimates2$`Known Costs UID`))
  
# Declare necessary variables
  sim_output_A_FRQ <- data.frame() 
  sim_output_B_FRQ <- data.frame()
  sim_output_C_FRQ <- data.frame()
  sim_output_A <- data.frame()
  sim_output_B <- data.frame()
  sim_output_C <- data.frame()
  sim_output_A_ICC <- data.frame()
  sim_output_B_ICC <- data.frame()
  sim_output_C_ICC <- data.frame()
  sim_output_A_RCC <- data.frame()
  sim_output_B_RCC <- data.frame()
  sim_output_C_RCC <- data.frame()
  sim_output_Bens <- data.frame()
  sim_output_Costs <- data.frame()

# Convert estimates from Frequency Formats to decimal / percentage ----
  # Plan A
  freq_form <- gEstimates$`Plan A Loss Event Frequency (LEF) Lower Bound`
  freq_form <- str_split(freq_form, " in ", n=2, simplify = TRUE)
  perc_form <- as.numeric(freq_form[,1])/as.numeric(freq_form[,2])
  gEstimates$`Plan A Loss Event Frequency (LEF) Lower Bound` <- perc_form
  
  freq_form <- gEstimates$`Plan A Loss Event Frequency (LEF) Most Likely`
  freq_form <- str_split(freq_form, " in ", n=2, simplify = TRUE)
  perc_form <- as.numeric(freq_form[,1])/as.numeric(freq_form[,2])
  gEstimates$`Plan A Loss Event Frequency (LEF) Most Likely` <- perc_form
  
  freq_form <- gEstimates$`Plan A Loss Event Frequency (LEF) Upper Bound`
  freq_form <- str_split(freq_form, " in ", n=2, simplify = TRUE)
  perc_form <- as.numeric(freq_form[,1])/as.numeric(freq_form[,2])
  gEstimates$`Plan A Loss Event Frequency (LEF) Upper Bound` <- perc_form
  
  # Plan B
  freq_form <- gEstimates$`Plan B Loss Event Frequency (LEF) Lower Bound`
  freq_form <- str_split(freq_form, " in ", n=2, simplify = TRUE)
  perc_form <- as.numeric(freq_form[,1])/as.numeric(freq_form[,2])
  gEstimates$`Plan B Loss Event Frequency (LEF) Lower Bound` <- perc_form
  
  freq_form <- gEstimates$`Plan B Loss Event Frequency (LEF) Most Likely`
  freq_form <- str_split(freq_form, " in ", n=2, simplify = TRUE)
  perc_form <- as.numeric(freq_form[,1])/as.numeric(freq_form[,2])
  gEstimates$`Plan B Loss Event Frequency (LEF) Most Likely` <- perc_form
  
  freq_form <- gEstimates$`Plan B Loss Event Frequency (LEF) Upper Bound`
  freq_form <- str_split(freq_form, " in ", n=2, simplify = TRUE)
  perc_form <- as.numeric(freq_form[,1])/as.numeric(freq_form[,2])
  gEstimates$`Plan B Loss Event Frequency (LEF) Upper Bound` <- perc_form
  
  # Plan C
  freq_form <- gEstimates$`Plan C Loss Event Frequency (LEF) Lower Bound`
  freq_form <- str_split(freq_form, " in ", n=2, simplify = TRUE)
  perc_form <- as.numeric(freq_form[,1])/as.numeric(freq_form[,2])
  gEstimates$`Plan C Loss Event Frequency (LEF) Lower Bound` <- perc_form
  
  freq_form <- gEstimates$`Plan C Loss Event Frequency (LEF) Most Likely`
  freq_form <- str_split(freq_form, " in ", n=2, simplify = TRUE)
  perc_form <- as.numeric(freq_form[,1])/as.numeric(freq_form[,2])
  gEstimates$`Plan C Loss Event Frequency (LEF) Most Likely` <- perc_form
  
  freq_form <- gEstimates$`Plan C Loss Event Frequency (LEF) Upper Bound`
  freq_form <- str_split(freq_form, " in ", n=2, simplify = TRUE)
  perc_form <- as.numeric(freq_form[,1])/as.numeric(freq_form[,2])
  gEstimates$`Plan C Loss Event Frequency (LEF) Upper Bound` <- perc_form
```

```{r simulation, include=FALSE}
  
# Simulate Plan A FREQUENCY (Monte Carlo)
sim_output_A_FRQ <- monterlo(
  n_scens = n_scens,
  n_perms = n_perms,
  prb = rep(1,n_scens),
  mn = gEstimates$`Plan A Loss Event Frequency (LEF) Lower Bound`,
  ml = gEstimates$`Plan A Loss Event Frequency (LEF) Most Likely`,
  mx = gEstimates$`Plan A Loss Event Frequency (LEF) Upper Bound`,
  out_var = sim_output_A_FRQ)

# Simulate Plan B FREQUENCY (Monte Carlo)
sim_output_B_FRQ <- monterlo(
  n_scens = n_scens,
  n_perms = n_perms,
  prb = rep(1,n_scens),
  mn = gEstimates$`Plan B Loss Event Frequency (LEF) Lower Bound`,
  ml = gEstimates$`Plan B Loss Event Frequency (LEF) Most Likely`,
  mx = gEstimates$`Plan B Loss Event Frequency (LEF) Upper Bound`,
  out_var = sim_output_B_FRQ)

# Simulate Plan C FREQUENCY (Monte Carlo)
sim_output_C_FRQ <- monterlo(
  n_scens = n_scens,
  n_perms = n_perms,
  prb = rep(1,n_scens),
  mn = gEstimates$`Plan C Loss Event Frequency (LEF) Lower Bound`,
  ml = gEstimates$`Plan C Loss Event Frequency (LEF) Most Likely`,
  mx = gEstimates$`Plan C Loss Event Frequency (LEF) Upper Bound`,
  out_var = sim_output_C_FRQ)

# Load Frequency means into memory
FRQ_mean <- colMeans(sim_output_A_FRQ)
FRQ_mean <- cbind(FRQ_mean,colMeans(sim_output_B_FRQ))
FRQ_mean <- cbind(FRQ_mean,colMeans(sim_output_C_FRQ))
FRQ_mean <- as.data.frame(FRQ_mean)
colnames(FRQ_mean) <- c("LEF-A","LEF-B","LEF-C")

# Simulate Plan A MAGNITUDE & given FREQUENCY simulated in previous step (Monte Carlo)
  sim_output_A <- monterlo(
    n_scens = n_scens,
    n_perms = n_perms,
    prb = FRQ_mean$`LEF-A`,
    mn = gEstimates$`Plan A Loss Magnitude (LM) Lower Bound`,
    ml = gEstimates$`Plan A Loss Magnitude (LM) Most Likely`,
    mx = gEstimates$`Plan A Loss Magnitude (LM) Upper Bound`,
    out_var = sim_output_A)
  
# Simulate Plan B MAGNITUDE & given FREQUENCY simulated in previous step (Monte Carlo)
  sim_output_B <- monterlo(
    n_scens = n_scens,
    n_perms = n_perms,
    prb = FRQ_mean$`LEF-B`,
    mn = gEstimates$`Plan B Loss Magnitude (LM) Lower Bound`,
    ml = gEstimates$`Plan B Loss Magnitude (LM) Most Likely`,
    mx = gEstimates$`Plan B Loss Magnitude (LM) Upper Bound`,
    out_var = sim_output_B)
  
# Simulate Plan C MAGNITUDE & given FREQUENCY simulated in previous step (Monte Carlo)
  sim_output_C <- monterlo(
    n_scens = n_scens,
    n_perms = n_perms,
    prb = FRQ_mean$`LEF-C`,
    mn = gEstimates$`Plan C Loss Magnitude (LM) Lower Bound`,
    ml = gEstimates$`Plan C Loss Magnitude (LM) Most Likely`,
    mx = gEstimates$`Plan C Loss Magnitude (LM) Upper Bound`,
    out_var = sim_output_C)
  
  # Simulate Initial Control Costs
    # Simulate Plan A initial CONTROL Costs
    sim_output_A_ICC <- monterlo(
      n_scens = n_scens,
      n_perms = n_perms,
      prb = rep(1,n_scens),
      mn = gEstimates$`Plan A Initial Control Cost Lower Bound`,
      ml = gEstimates$`Plan A Initial Control Cost Most Likely`,
      mx = gEstimates$`Plan A Initial Control Cost Upper Bound`,
      out_var = sim_output_A_ICC)
    
    # Simulate Plan B  initial CONTROL Costs
    sim_output_B_ICC <- monterlo(
      n_scens = n_scens,
      n_perms = n_perms,
      prb = rep(1,n_scens),
      mn = gEstimates$`Plan B Initial Control Cost Lower Bound`,
      ml = gEstimates$`Plan B Initial Control Cost Most Likely`,
      mx = gEstimates$`Plan B Initial Control Cost Upper Bound`,
      out_var = sim_output_B_ICC)
    
    # Simulate Plan C initial CONTROL Costs
    sim_output_C_ICC <- monterlo(
      n_scens = n_scens,
      n_perms = n_perms,
      prb = rep(1,n_scens),
      mn = gEstimates$`Plan C Initial Control Cost Lower Bound`,
      ml = gEstimates$`Plan C Initial Control Cost Most Likely`,
      mx = gEstimates$`Plan C Initial Control Cost Upper Bound`,
      out_var = sim_output_C_ICC)
    
    # Simulate Recurring Control Costs
    # Simulate Plan A recurring CONTROL Costs
    sim_output_A_RCC <- monterlo(
      n_scens = n_scens,
      n_perms = n_perms,
      prb = rep(1,n_scens),
      mn = gEstimates$`Plan A Recurring Control Cost Lower Bound`,
      ml = gEstimates$`Plan A Recurring Control Cost Most Likely`,
      mx = gEstimates$`Plan A Recurring Control Cost Upper Bound`,
      out_var = sim_output_A_RCC)
    
    # Simulate Plan B recurring CONTROL Costs
    sim_output_B_RCC <- monterlo(
      n_scens = n_scens,
      n_perms = n_perms,
      prb = rep(1,n_scens),
      mn = gEstimates$`Plan B Recurring Control Cost Lower Bound`,
      ml = gEstimates$`Plan B Recurring Control Cost Most Likely`,
      mx = gEstimates$`Plan B Recurring Control Cost Upper Bound`,
      out_var = sim_output_B_RCC)
    
    # Simulate Plan C recurring CONTROL Costs
    sim_output_C_RCC <- monterlo(
      n_scens = n_scens,
      n_perms = n_perms,
      prb = rep(1,n_scens),
      mn = gEstimates$`Plan C Recurring Control Cost Lower Bound`,
      ml = gEstimates$`Plan C Recurring Control Cost Most Likely`,
      mx = gEstimates$`Plan C Recurring Control Cost Upper Bound`,
      out_var = sim_output_C_RCC)
  
    # Simulate Known Benefits
    sim_output_Bens <- monterlo(
      n_scens = n_bens,
      n_perms = n_perms,
      prb = as.numeric(na.omit(gEstimates2$`Benefits Probability`)),
      mn = as.integer(na.omit(gEstimates2$`Benefits Lower Bound`)),
      ml = as.integer(na.omit(gEstimates2$`Benefits Most Likely`)),
      mx = as.integer(na.omit(gEstimates2$`Benefits Upper Bound`)),
      out_var = sim_output_Bens)
    
    # Simulated Known Costs
    sim_output_Costs <- monterlo(
      n_scens = n_costs,
      n_perms = n_perms,
      prb = rep(1,n_scens),
      mn = gEstimates2$`Known Costs Lower Bound`,
      ml = gEstimates2$`Known Costs Most Likely`,
      mx = gEstimates2$`Known Costs Upper Bound`,
      out_var = sim_output_Costs)
```

```{r evaluations, include=FALSE}
# Add header rows to simulation outputs
  # headers for loss outputs
  colnames(sim_output_A) <- as.character(paste("Risk-",1:n_scens,sep = ""))
  colnames(sim_output_B) <- as.character(paste("Risk-",1:n_scens,sep = ""))
  colnames(sim_output_C) <- as.character(paste("Risk-",1:n_scens,sep = ""))
  # headers for initial control cost outputs
  colnames(sim_output_A_ICC) <- as.character(paste("Risk-",1:n_scens,sep = ""))
  colnames(sim_output_B_ICC) <- as.character(paste("Risk-",1:n_scens,sep = ""))
  colnames(sim_output_C_ICC) <- as.character(paste("Risk-",1:n_scens,sep = ""))
  # headers for recurring control cost outputs
  colnames(sim_output_A_RCC) <- as.character(paste("Risk-",1:n_scens,sep = ""))
  colnames(sim_output_B_RCC) <- as.character(paste("Risk-",1:n_scens,sep = ""))
  colnames(sim_output_C_RCC) <- as.character(paste("Risk-",1:n_scens,sep = ""))
  # headers for benefit outputs
  colnames(sim_output_Bens) <- as.character(paste("benefit-",1:n_bens,sep = ""))
  # headers for benefit outputs
  colnames(sim_output_Costs) <- as.character(paste("cost-",1:n_costs,sep = ""))

# Load the mean of all columns into memory
  # load Loss Magnitude (LM) means into memory
  risk_mean <- colMeans(sim_output_A)
  risk_mean <- cbind(risk_mean,colMeans(sim_output_B))
  risk_mean <- cbind(risk_mean,colMeans(sim_output_C))
  risk_mean <- as.data.frame(risk_mean)
  colnames(risk_mean) <- c("PLAN-A","PLAN-B","PLAN-C")
  
  # load Initial control cost (ICC) means into memory
  control_mean <- colMeans(sim_output_A_ICC)
  control_mean <- cbind(control_mean,colMeans(sim_output_B_ICC))
  control_mean <- cbind(control_mean,colMeans(sim_output_C_ICC))

  # load recurring control cost (RCC) means into memory
  control_mean <- cbind(control_mean,colMeans(sim_output_A_RCC))
  control_mean <- cbind(control_mean,colMeans(sim_output_B_RCC))
  control_mean <- cbind(control_mean,colMeans(sim_output_C_RCC))
  
  # convert control means object to dataframe and name columns
  control_mean <- as.data.frame(control_mean)
  colnames(control_mean) <- c("ICC-A","ICC-B","ICC-C","RCC-A","RCC-B","RCC-C")
  
  # load Benefit means into memory
  Benefit_mean <- colMeans(sim_output_Bens)
  Benefit_mean <- as.data.frame(Benefit_mean)
  # eval recurring
  Benefit_mean <- cbind(Benefit_mean,Benefit_mean*gEstimates2$`Benefits Recurring_Ben`)
  colnames(Benefit_mean) <- c("Benefit","Recurring_Benefit")
  
  # load Costs means into memory
  Cost_mean <- colMeans(sim_output_Costs)
  Cost_mean <- as.data.frame(Cost_mean)
  # eval recurring
  Cost_mean <- cbind(Cost_mean,Cost_mean*gEstimates2$`Known Costs Recurring Expense`)
  colnames(Cost_mean) <- c("Cost","Recurring_Cost")
  
# Eval ----
  evals <- data.frame()
  REL_AvB <- risk_mean$`PLAN-A` - risk_mean$`PLAN-B`
  REL_AvC <- risk_mean$`PLAN-A` - risk_mean$`PLAN-C`
  ROSI_AvB <- na_if(na_if(REL_AvB/control_mean$`ICC-B`-1,"Inf"),"-Inf")
  ROSI_AvC <- na_if(na_if(REL_AvC/control_mean$`ICC-C`-1,"Inf"),"-Inf")
  NET_AvB <- na_if(na_if(ROSI_AvB*control_mean$`ICC-B`,"Inf"),"-Inf")
  NET_AvC <- na_if(na_if(ROSI_AvC*control_mean$`ICC-C`,"Inf"),"-Inf")
  
  # Forcasts
    # Year 1
      # A: Benefits - Costs - Loss_magn.
        NET_A_Year1 <- sum(Benefit_mean$Benefit) - sum(Cost_mean$Cost) - risk_mean$`PLAN-A`
      # B: Benefits_init - Costs_init - Loss Magn. - Ctrl_cost_init + Reduction_In_exp_losses
        NET_B_Year1 <- sum(Benefit_mean$Benefit) - sum(Cost_mean$Cost) - risk_mean$`PLAN-B` - control_mean$`ICC-B` + REL_AvB
      # C: Benefits_init - Costs_init - Loss Magn. - Ctrl_cost_init + Reduction_In_exp_losses
        NET_C_Year1 <- sum(Benefit_mean$Benefit) - sum(Cost_mean$Cost) - risk_mean$`PLAN-C` - control_mean$`ICC-C` + REL_AvC
        
    # Year 2
      # A: (((Benefits+Benefits_recurring)-(Costs-Costs_Recurring))-(Loss_Magn*2))
        NET_A_Year2 <- (((sum(Benefit_mean$Benefit)+sum(Benefit_mean$Benefit_Recurring)) - (sum(Cost_mean$Cost-sum(Cost_mean$Cost_Recurring))) - risk_mean$`PLAN-A`*2))
        
      # B: (((Benefits+Benefits_recurring)-(Costs-Costs_Recurring))-(Loss_Magn*2-Initial_Ctrl_Cost+ReductionEL*2))-Ctrl_Costs_recurring
        NET_B_Year2 <- (((sum(Benefit_mean$Benefit)+sum(Benefit_mean$Benefit_Recurring)) - (sum(Cost_mean$Cost-sum(Cost_mean$Cost_Recurring))) - risk_mean$`PLAN-B`*2 - control_mean$`ICC-B` + REL_AvB*2)) - control_mean$`RCC-B`
        
      # C: (((Benefits+Benefits_recurring)-(Costs-Costs_Recurring))-(Loss_Magn*2-Initial_Ctrl_Cost+ReductionEL*2))-Ctrl_Costs_recurring
        NET_C_Year2 <- (((sum(Benefit_mean$Benefit)+sum(Benefit_mean$Benefit_Recurring)) - (sum(Cost_mean$Cost-sum(Cost_mean$Cost_Recurring))) - risk_mean$`PLAN-C`*2 - control_mean$`ICC-C` + REL_AvC*2)) - control_mean$`RCC-C`
        
    # Year 3
      # A: (Benefit+Benefit_recurring*2)-(Cost_initial+Cost_recurring*2)-Loss_magn*3-Ctrl_Cost_init)-Ctrl_Cost_recurring*2
        NET_A_Year3 <- (((sum(Benefit_mean$Benefit)+sum(Benefit_mean$Benefit_Recurring*2)) - (sum(Cost_mean$Cost-sum(Cost_mean$Cost_Recurring*2))) - risk_mean$`PLAN-A`*3 - control_mean$`ICC-A`)) - control_mean$`RCC-A`*2
        
      # B: (Benefit+Benefit_recurring*2)-(Cost_initial+Cost_recurring*2)-Loss_magn*3-Ctrl_Cost_init+ReductionEL*3)-Ctrl_Cost_recurring*2
        NET_B_Year3 <- (((sum(Benefit_mean$Benefit)+sum(Benefit_mean$Benefit_Recurring*2)) - (sum(Cost_mean$Cost-sum(Cost_mean$Cost_Recurring*2))) - risk_mean$`PLAN-A`*3 - control_mean$`ICC-B` + REL_AvB*3)) - control_mean$`RCC-B`*2
        
      # C: (Benefit+Benefit_recurring*2)-(Cost_initial+Cost_recurring*2)-Loss_magn*3-Ctrl_Cost_init+ReductionEL*3)-Ctrl_Cost_recurring*2
        NET_C_Year3 <- (((sum(Benefit_mean$Benefit)+sum(Benefit_mean$Benefit_Recurring*2)) - (sum(Cost_mean$Cost-sum(Cost_mean$Cost_Recurring*2))) - risk_mean$`PLAN-A`*3 - control_mean$`ICC-C` + REL_AvB*3)) - control_mean$`RCC-C`*2
      
  evals <- cbind(risk_mean,
                 control_mean,
                 REL_AvB,
                 REL_AvC,
                 ROSI_AvB,
                 ROSI_AvC,
                 NET_AvB,
                 NET_AvC,
                 NET_A_Year1,
                 NET_B_Year1,
                 NET_C_Year1,
                 NET_A_Year2,
                 NET_B_Year2,
                 NET_C_Year2,
                 NET_A_Year3,
                 NET_B_Year3,
                 NET_C_Year3
                 )

  # Year 1 Expected
    Expected_Benefits_y1 <- sum(Benefit_mean$Benefit)
    Expected_Implementation_Costs_y1 <- sum(Cost_mean$Cost)
    
    # Plan A
    Expected_Losses_A_y1 <- mean(risk_mean$`PLAN-A`)
    Expected_Mitigation_Costs_A_y1 <- mean(control_mean$`ICC-A`)
    Expected_Prevented_Loss_A_y1 <- 0
    Expected_Net_A_y1 <- mean(NET_A_Year1)
    
    # Plan B
    Expected_Losses_B_y1 <- mean(risk_mean$`PLAN-B`)
    Expected_Mitigation_Costs_B_y1 <- mean(control_mean$`ICC-B`)
    Expected_Prevented_Loss_B_y1 <- mean(REL_AvB)
    Expected_Net_B_y1 <- mean(NET_B_Year1)
    
    # Plan C
    Expected_Losses_C_y1 <- mean(risk_mean$`PLAN-C`)
    Expected_Mitigation_Costs_C_y1 <- mean(control_mean$`ICC-C`)
    Expected_Prevented_Loss_C_y1 <- mean(REL_AvC)
    Expected_Net_C_y1 <- mean(NET_C_Year1)
    
  # Year 2 Expected
    Expected_Benefits_y2 <- sum(Benefit_mean$Benefit)+sum(Benefit_mean$Recurring_Benefit)
    Expected_Implementation_Costs_y2 <- sum(Cost_mean$Cost)+sum(Cost_mean$Recurring_Cost)
    
    # Plan A
    Expected_Losses_A_y2 <- mean(risk_mean$`PLAN-A`)*2
    Expected_Mitigation_Costs_A_y2 <- mean(control_mean$`ICC-A`)+mean(control_mean$`RCC-A`)
    Expected_Prevented_Loss_A_y2 <- 0
    Expected_Net_A_y2 <- mean(NET_A_Year2)
    
    # Plan B
    Expected_Losses_B_y2 <- mean(risk_mean$`PLAN-B`)*2
    Expected_Mitigation_Costs_B_y2 <- mean(control_mean$`ICC-B`)+mean(control_mean$`RCC-B`)
    Expected_Prevented_Loss_B_y2 <- mean(REL_AvB)*2
    Expected_Net_B_y2 <- mean(NET_B_Year2)
    
    # Plan C
    Expected_Losses_C_y2 <- mean(risk_mean$`PLAN-C`)*2
    Expected_Mitigation_Costs_C_y2 <- mean(control_mean$`ICC-C`)+mean(control_mean$`RCC-C`)
    Expected_Prevented_Loss_C_y2 <- mean(REL_AvC)*2
    Expected_Net_C_y2 <- mean(NET_C_Year2)
    
  # Year 3 Expected
    Expected_Benefits_y3 <- sum(Benefit_mean$Benefit)+sum(Benefit_mean$Recurring_Benefit)*2
    Expected_Implementation_Costs_y3 <- sum(Cost_mean$Cost)+sum(Cost_mean$Recurring_Cost)*2
    
    # Plan A
    Expected_Losses_A_y3 <- mean(risk_mean$`PLAN-A`)*3
    Expected_Mitigation_Costs_A_y3 <- mean(control_mean$`ICC-A`)+mean(control_mean$`RCC-A`)*2
    Expected_Prevented_Loss_A_y3 <- 0
    Expected_Net_A_y3 <- mean(NET_A_Year3)
    
    # Plan B
    Expected_Losses_B_y3 <- mean(risk_mean$`PLAN-B`)*3
    Expected_Mitigation_Costs_B_y3 <- mean(control_mean$`ICC-B`)+mean(control_mean$`RCC-B`)*2
    Expected_Prevented_Loss_B_y3 <- mean(REL_AvB)*3
    Expected_Net_B_y3 <- mean(NET_B_Year3)
    
    # Plan C
    Expected_Losses_C_y3 <- mean(risk_mean$`PLAN-C`)*3
    Expected_Mitigation_Costs_C_y3 <- mean(control_mean$`ICC-C`)+mean(control_mean$`RCC-C`)*2
    Expected_Prevented_Loss_C_y3 <- mean(REL_AvC)*3
    Expected_Net_C_y3 <- mean(NET_C_Year3)
  
  # Build forcast tables
  # Plan A 3-year table
  Plan_A_Expected <- as.data.frame(rbind(
    Expected_Benefits_y1,
    Expected_Implementation_Costs_y1,
    Expected_Losses_A_y1,
    Expected_Mitigation_Costs_A_y1,
    Expected_Prevented_Loss_A_y1,
    Expected_Net_A_y1))
  Plan_A_Expected$Year_2 <- rbind(
    Expected_Benefits_y2,
    Expected_Implementation_Costs_y2,
    Expected_Losses_A_y2,
    Expected_Mitigation_Costs_A_y2,
    Expected_Prevented_Loss_A_y2,
    Expected_Net_A_y2)
  Plan_A_Expected$Year_3 <- rbind(
    Expected_Benefits_y3,
    Expected_Implementation_Costs_y3,
    Expected_Losses_A_y3,
    Expected_Mitigation_Costs_A_y3,
    Expected_Prevented_Loss_A_y3,
    Expected_Net_A_y3)
  
  # Plan B 3-year table
  Plan_B_Expected <- as.data.frame(rbind(
    Expected_Benefits_y1,
    Expected_Implementation_Costs_y1,
    Expected_Losses_B_y1,
    Expected_Mitigation_Costs_B_y1,
    Expected_Prevented_Loss_B_y1,
    Expected_Net_B_y1))
  Plan_B_Expected$Year_2 <- rbind(
    Expected_Benefits_y2,
    Expected_Implementation_Costs_y2,
    Expected_Losses_B_y2,
    Expected_Mitigation_Costs_B_y2,
    Expected_Prevented_Loss_B_y2,
    Expected_Net_B_y2)
  Plan_B_Expected$Year_3 <- rbind(
    Expected_Benefits_y3,
    Expected_Implementation_Costs_y3,
    Expected_Losses_B_y3,
    Expected_Mitigation_Costs_B_y3,
    Expected_Prevented_Loss_B_y3,
    Expected_Net_B_y3)
  
  # Plan c 3-year table
  Plan_C_Expected <- as.data.frame(rbind(
    Expected_Benefits_y1,
    Expected_Implementation_Costs_y1,
    Expected_Losses_C_y1,
    Expected_Mitigation_Costs_C_y1,
    Expected_Prevented_Loss_C_y1,
    Expected_Net_C_y1))
  Plan_C_Expected$Year_2 <- rbind(
    Expected_Benefits_y2,
    Expected_Implementation_Costs_y2,
    Expected_Losses_C_y2,
    Expected_Mitigation_Costs_C_y2,
    Expected_Prevented_Loss_C_y2,
    Expected_Net_C_y2)
  Plan_C_Expected$Year_3 <- rbind(
    Expected_Benefits_y3,
    Expected_Implementation_Costs_y3,
    Expected_Losses_C_y3,
    Expected_Mitigation_Costs_C_y3,
    Expected_Prevented_Loss_C_y3,
    Expected_Net_C_y3)
  
  # Name rows and columns
  row.names(Plan_A_Expected) <- c("Benefits","Costs","Loss","Mitigation Costs","Prevented Loss","Net")
  colnames(Plan_A_Expected) <- c("Year 1", "Year 2","Year 3")
  row.names(Plan_B_Expected) <- c("Benefits","Costs","Loss","Mitigation Costs","Prevented Loss","Net")
  colnames(Plan_B_Expected) <- c("Year 1", "Year 2","Year 3")
  row.names(Plan_C_Expected) <- c("Benefits","Costs","Loss","Mitigation Costs","Prevented Loss","Net")
  colnames(Plan_C_Expected) <- c("Year 1", "Year 2","Year 3")
  
```
  
```{r procesing_for_visuals, include=FALSE}
  #Data Prep for visualisations
  # Density Plot 1
  df <- t(risk_mean)
  df.m <- melt(df)
  colnames(df.m) <- as.character(c("plan","risk","loss"))
  mu <- ddply(df.m, "plan", summarise, grp.mean=mean(loss))
  df.m$plan <- factor(df.m$plan, levels = c("PLAN-C", "PLAN-B", "PLAN-A"))
  mu$plan <- factor(mu$plan, levels = c("PLAN-C", "PLAN-B", "PLAN-A"))
  
  # Density Plot 2 (costs)
  df2 <- t(Cost_mean)
  df.m2 <- melt(sim_output_Costs)
  colnames(df.m2) <- as.character(c("cost_name","cost_amt"))
  mu2 <- ddply(df.m2, "cost_name", summarise, grp.mean=mean(cost_amt))
  df.m2$cost_name <- factor(df.m2$cost_name)
  mu2$cost_name <- factor(mu2$cost_name)
  
  # Density Plot 3 (bens)
  df3 <- t(Benefit_mean)
  df.m3 <- melt(sim_output_Bens)
  colnames(df.m3) <- as.character(c("ben_name","ben_amt"))
  mu3 <- ddply(df.m3, "ben_name", summarise, grp.mean=mean(ben_amt))
  df.m3$ben_name <- factor(df.m3$ben_name)
  mu3$cost_name <- factor(mu3$ben_name)
  
# For per plan ECDF
  loss_ecdf <- ddply(df.m, c("plan"), mutate, ecdf = ecdf(loss)(unique(loss))*length(loss))
  # To invert the per plan ECDF
  loss_ecdf_2 <- ddply(loss_ecdf, "plan", mutate, ecdf = scale(ecdf,center=min(ecdf),scale=diff(range(ecdf))))
  
  # Net amounts and graphs
  Nets <- rbind(Plan_A_Expected[6,], Plan_B_Expected[6,], Plan_C_Expected[6,])
  row.names(Nets) <- c("PLAN-C", "PLAN-B", "PLAN-A")
  Netsm <- melt(t(Nets),id = 0)
  Netsm$Net <- as.numeric(Netsm$value)
  Netsm$Net <- dollar(as.numeric(Netsm$Net))
  colnames(Netsm) <- c("Year", "Plan", "Net")
  
  colnames(gScope) <- c("Included","Excluded","Included","Excluded","Included","Excluded","Included","Excluded","Included","Excluded")
  
  
```

***
GPM Personal - Corey Neskey - 1/25/20

Executive Summary {.storyboard}
=====================================

### **Background** {data-commentary-width=500}

![](graph(1).png)

***

- The USB scenarios considered involve removing a security control that has been in place at Derp Corp since VirtualDerp was set up but enables personnel an easier method of file export.

- The SuperCloud scenarios considered do not involve removal of security controls but affords a less convenient method of file export.

### **Scope** {data-commentary-width=500}

```{r scope_table2}
options(knitr.kable.NA = '')
kable(gScope, format = "html", caption = "Scope Table") %>%
  kable_styling(bootstrap_options = "striped",
                full_width = F) %>%
  add_header_above(c(
                     "Assets at risk"	= 2,
                     "Containers/Points of attack"= 2,
                     "Threat communities"= 2,
                     "Threat Types"= 2,
                     "Effects"= 2
                     ))
```

***
scopedy scope scope


### **Recommendation**  It is recommended that Derp Corp proceed with Plan B. {data-commentary-width=500}

Table of visual highlighting Plan B...

***

- Although the number of risks is greater, Derp Corp’s ability to reduce the probability, impact, and uncertainty of the controls associated with the SuperCloud Scenario 2 result in the least estimated risk.
- the use of SuperCloud does not necessitate the additional expense and complexity of ongoing purchasing and encrypting of USB storage drives.

* “Plan B: Dedicated, trained staff, controlled SuperCloud access folders, folder access expiration, “hardened” workstations, and minimum access CoreDB and file share accounts.”


### **Next Steps** The CIO of PIZZA CORP. Kitchen has requested that PIZZA CORP. Kitchen IT personnel provide the analyst with the following information after review of this report.{data-commentary-width=500}

- changes to scope as defined in Scope section of this report
- controls from Recommendations section that will be implemented
- subsequent review of the revised assessment inclusive of aforementioned changes and controls selected

***

- All information collected, journaling of activities, FAIR factors, and probabilistic risk model
representing these changes are retained in a Box folder shared with the PIZZA CORP. Kitchen
CIO.

- The remainder of this report outlines the analysis in more depth for reference, validation, and
welcome scrutiny.




Analysis {.storyboard}
=====================================

### **Projection**  The net value after factoring in costs, benefits, losses, and mitigation costs over 1 year, 3 year, and 5 years. {data-commentary-width=800}


**Plan A Expected**

```{r plan_a_expected}
a_exp <- formattable(mutate_all(Plan_A_Expected,dollar))
row.names(a_exp) <- row.names(Plan_A_Expected)
a_exp
```


**Plan B Expected**

```{r plan_b_expected}
b_exp <- formattable(mutate_all(Plan_B_Expected,dollar))
row.names(b_exp) <- row.names(Plan_B_Expected)
b_exp
```


**Plan C Expected**
 
```{r plan_c_expected}
c_exp <- formattable(mutate_all(Plan_C_Expected,dollar))
row.names(c_exp) <- row.names(Plan_C_Expected)
c_exp
```

***

```{r line_plot}
ggplot() +
  geom_line(data=Netsm, aes(x=Year,y=Net,group=Plan,colour=Plan))+
  geom_point(data=Netsm, aes(x=Year,y=Net,group=Plan,colour=Plan))+
  geom_hline(aes(yintercept = 0))+
  labs(
      title="Expected Net Value",
      subtitle = "Benefits minus Costs,Losses,Mitigation Costs, and Prevented Losses)",
      y = "Net Value")+
  scale_fill_viridis(discrete=TRUE)+
  scale_color_viridis(discrete=TRUE)

```

### **Benefits**  Parameters provided by experts to approximate benefits of this project {data-commentary-width=500}


***
```{r benefits_table}
options(knitr.kable.NA = '')
derp <- gEstimates2[,1:8]
kable(derp, format = "html", caption = "Benefits Table") %>%
  kable_styling(bootstrap_options = "striped",
                full_width = F)
```

### **Costs** Parameters provided by experts to approximate the costs of this project. {data-commentary-width=500}

***
```{r costs_table}
options(knitr.kable.NA = '')
derp <- gEstimates2[,9:15]
kable(derp, format = "html", caption = "Costs Table") %>%
  kable_styling(bootstrap_options = "striped",
                full_width = F)
```


### Scenarios {data-commentary-width=500}
```{r Scenarios_table}
options(knitr.kable.NA = '')
derp <- gEstimates[,1:7]
kable(derp, format = "html", caption = "Scenarios Table") %>%
  kable_styling(bootstrap_options = "striped",
                full_width = F)
```

***

- nn scenarios were generated by exausting...
- nn were disregarded.

### ECDF {data-commentary-width=500}

```{r ECDF_plot}
  # Vis ####
  # # Inverse Empirical Cumulative Distribution Function (ECDF)
  ggplotly(ggplot(loss_ecdf_2,  mapping = aes(x = loss, y = 1-ecdf, colour = plan)) +
    geom_line()+
    labs(
      title="Simulated Loss Output",
      subtitle = "Over a 12 month period",
      x = "Magnitude of loss or greater",
      y = "Chance of loss or greater")+
    scale_x_continuous(labels = dollar_format())+
    scale_y_continuous(labels = percent_format())+
    scale_fill_viridis(discrete=TRUE)+
    scale_color_viridis(discrete=TRUE))

```

***
ECDF...

### Density {data-commentary-width=500}

```{r density_plot}
  # # Density Plot
  ggplotly(ggplot(df.m, aes(x=loss, color=plan, fill=plan)) +
    geom_density(alpha=0.6) +
    geom_vline(data=mu, aes(xintercept=grp.mean, color=plan),
               linetype="dashed") +
    theme_classic() +
    theme(legend.position="top") +
    labs(
      title="Simulated Loss Output",
      subtitle = "Over a 12 month period",
      x = "Loss",
      y = "Density") +
    scale_x_continuous(labels = dollar_format())+
    scale_fill_viridis(discrete=TRUE)+
    scale_color_viridis(discrete=TRUE))

```

***
Density...

### Violin {data-commentary-width=500}

```{r violin_plot}
# # Vertical Violin Plot
  ggplotly(ggplot(data = df.m, aes(x=plan, y=loss)) +
    geom_violin(aes(fill = factor(plan))) +
    labs(
      title="Simulated Loss Output",
      subtitle = "Over a 12 month period",
      x = "Control Scenarios",
      y = "Loss") +
    scale_y_continuous(labels = dollar_format())+
    scale_fill_viridis(discrete=TRUE)+
    scale_color_viridis(discrete=TRUE))
```

***
Violin...

### Swarm {data-commentary-width=500}

```{r swarm_plot}
# # Vertical beeswarm Plot
  ggplotly(ggplot(data = df.m, aes(x=plan, y=loss,color = factor(plan))) +
             geom_beeswarm()+
    labs(
      title="Simulated Loss Output",
      subtitle = "Over a 12 month period",
      x = "Control Scenarios",
      y = "Loss") +
    scale_y_continuous(labels = dollar_format())+
    scale_fill_viridis(discrete=TRUE)+
    scale_color_viridis(discrete=TRUE))
```

***
Swarm...

### Box {data-commentary-width=500}

```{r box_plot}
# # Horizontal Box Plot
  ggplotly(ggplot(data = df.m, aes(x=plan, y=loss)) +
    geom_boxplot(outlier.colour = "black", outlier.shape = 1, color=c("#4b0082","lightseagreen","gold")) +
    labs(
      title="Simulated Loss Output",
      subtitle = "Over a 12 month period",
      x = "Control Scenarios",
      y = "Loss") +
    scale_y_continuous(labels = dollar_format()) +
    expand_limits(y = c(0,df.m$loss+(df.m$loss*.05))) +
    coord_flip())
```

***
Box...

### Ridge {data-commentary-width=500}

```{r ridge_plot}
# # Horizontal Ridge Density Plot
  ggplot(df.m, aes(x=loss, y=plan, fill=plan)) +
    geom_density_ridges(scale = .9, alpha = .8)+
    geom_vline(data=mu, aes(xintercept=grp.mean, color=plan),
               linetype="solid", show.legend = F) +
    labs(
      caption = "Vertical lines are loss means",
      title="Simulated Loss Output",
      subtitle = "Over a 12 month period",
      x = "Loss",
      y = "Density") +
    scale_x_continuous(labels = dollar_format())+
    scale_fill_viridis(discrete=TRUE) +
    scale_color_viridis(discrete=TRUE) +
    theme_ridges( grid = FALSE)
```

***

Ridge